The Rapid Cycleway Prioritisation Tool

### 2020-06-15 rapid-slides.Rmd
Update slides, close cyipt/icicle#18

---
title: "The Rapid Cycleway Prioritisation Tool"
subtitle: "🛣🚲🚀<br/>methods and results<br/>[cyipt.bike/rapid](https://www.cyipt.bike/rapid/)"
author: "Robin Lovelace and Joey Talbot"
institute: "University of Leeds, [Institute for Transport Studies](https://environment.leeds.ac.uk/transport). [Source code](https://github.com/cyipt/popupCycleways/blob/master/rapid-slides.Rmd)."
date: "Green Transport Recovery Series, 2020-06-17"
output:
  xaringan::moon_reader:
    css: [default, robot, robot-fonts]
    lib_dir: libs
    nature: 
      beforeInit: "https://platform.twitter.com/widgets.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r, engine='bash', eval=FALSE, echo=FALSE}
cp rapid-slides.html popupCycleways/v1/slides/index.html
cp -Rv libs popupCycleways/v1/slides/
cd popupCycleways
git status
git add -A
git commit -am 'Add slides'
git push
cd -
```

@@

1) reduced capacity on public transport 2) need for space so physical distancing guidelines can be followed
3) healthy restart 4) need to act fast

@@

Plans from Leeds City Council responding to national [guidance](https://www.gov.uk/government/publications/reallocating-road-space-in-response-to-covid-19-statutory-guidance-for-local-authorities) and [funding](https://www.gov.uk/government/news/2-billion-package-to-create-new-era-for-cycling-and-walking) for 'pop-up' cycleways:

@@

![](https://raw.githubusercontent.com/cyipt/popupCycleways/master/figures/results-cycleways-leeds.png)

@@

@@

![](https://raw.githubusercontent.com/cyipt/popupCycleways/master/figures/results-cohesive-leeds.png)

@@

- Narrow focus on road space reallocation options
- No economic appraisal
  - Use the Active Mode Appraisal Toolkit ([AMAT](https://www.gov.uk/government/publications/tag-social-and-distributional-impacts-worksheets)) 
- The best locations for new cycleways may not always have space
  - Search for parallel routes, which may be available
- Many options not in top routes
  - see cohesive network and look for other option
- The road network data is from 2017 and widths are estimates
  - Compare with real world knowledge
- Only work and school trips included
  - Use local knowledge of new developments and other 'trip attractors
- Prioritises routes in large cities in authorities with multiple settlements
  - Use alternative sources of information, including the PCT

@@

# Next steps

- Many future directions of travel including evidence to support [Low Traffic Neighbourhoods](https://github.com/luukvdmeer/sfnetworks/issues/13)

@@

>>>>

---
title: "The Rapid Cycleway Prioritisation Tool"
subtitle: "methods and results<br/>[cyipt.bike/rapid](https://www.cyipt.bike/rapid/)"
author: "Robin Lovelace and Joey Talbot"
institute: "University of Leeds, [Institute for Transport Studies](https://environment.leeds.ac.uk/transport).<br/>Publicly available [slides](https://www.cyipt.bike/rapid/slides/). Reproducible [code](https://github.com/cyipt/popupCycleways/blob/master/rapid-slides.Rmd). Paper [preprint](https://osf.io/7wjb6/)."
date: "Green Transport Recovery Series, 2020-06-17"
output:
  xaringan::moon_reader:
    css: [default, robot, robot-fonts]
    lib_dir: libs
    nature: 
      beforeInit: "https://platform.twitter.com/widgets.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r, engine='bash', eval=FALSE, echo=FALSE}
# 🛣🚲🚀
cp rapid-slides.html popupCycleways/v1/slides/index.html
cp -Rv libs popupCycleways/v1/slides/
cd popupCycleways
git status
git add -A
git commit -am 'Add slides'
git push
cd -
```

@@

1) reduced capacity on public transport 2) need for space so physical distancing guidelines can be followed
3) healthy restart 4) need to act fast. Image credit: [TfL](https://twitter.com/W_Bradley/status/1268836932219478016).

@@

Plans from Leeds City Council responding to national [guidance](https://www.gov.uk/government/publications/reallocating-road-space-in-response-to-covid-19-statutory-guidance-for-local-authorities) and [funding](https://www.gov.uk/government/news/2-billion-package-to-create-new-era-for-cycling-and-walking) for 'pop-up' cycleways (image credit: [Leeds City Council](https://news.leeds.gov.uk/news/leeds-city-council-announces-emergency-walking-and-cycling-plans-in-response-to-covid-19)):

@@

![](https://raw.githubusercontent.com/cyipt/popupCycleways/master/figures/results-cycleways-leeds.png)
Image credit: [Rapid Cycleway Prioritisation Tool](https://www.cyipt.bike/rapid/)

@@

Image credit: [Rapid Cycleway Prioritisation Tool](https://www.cyipt.bike/rapid/)

@@

![](https://raw.githubusercontent.com/cyipt/popupCycleways/master/figures/results-cohesive-leeds.png)
Image credit: [Rapid Cycleway Prioritisation Tool](https://www.cyipt.bike/rapid/)

@@

- Narrow focus on road space reallocation options
- No economic appraisal
  - Use the Active Mode Appraisal Toolkit ([AMAT](https://www.gov.uk/government/publications/tag-social-and-distributional-impacts-worksheets)) 
- The best locations for new cycleways may not always have space
  - Search for parallel routes, which may be available
- Many options not in top routes
  - see cohesive network and look for other option
- The road network data is from 2017 and widths are estimates
  - Compare with real world knowledge
- Only work and school trips included
  - Use local knowledge of new developments and other 'trip attractors
- Prioritises routes in large cities in authorities with multiple settlements
  - Use alternative sources of information, including the PCT
  - Do additional analysis, e.g. based on data downloaded from the Rapid tool or the PCT

@@

## Next steps

Many future directions of travel including evidence to support [Low Traffic Neighbourhoods](https://github.com/luukvdmeer/sfnetworks/issues/13)

@@

<!-- CWIS technical reports -->
<!-- Cost per intervention type -->
